### 2016-03-11 manuscript.Rnw
fix and add citations

In ecology, the development of the field of community phylogenetics
\citep{Webb2002} has created a need for researchers to have access to the
evolutionary relationships of species making up communities. The relative
contributions of the role of the environment (e.g., habitat filtering), and of
biotic interactions (e.g., competitive exclusion), are inferred from the
distribution of taxa on a phylogeny composed from species occurring at larger
spatial scale. R packages and other software have been developed to generate
phylogenies from species lists using taxonomic information or DNA
sequences. These phylogenies can then be used for community phylogenetics
analyses (e.g., \citep{Pearse2013}, \citep{Kembel}, \citep{Webb}), but as OTL
becomes more comprehensive, it could become a valuable resource for ecologists.

@@

<<get_cats, purl=FALSE, fig.cap="Tree from \\citealt{Johnson2006} obtained from OTL">>=
cat_studies <- studies_find_studies(property = "ot:focalCladeOTTTaxonName",
                                    value = "felidae")
cat_studies
@

>>>>

In ecology, the development of the field of community phylogenetics
\citep{Webb2002} has created a need for researchers to have access to the
evolutionary relationships of species making up communities. The relative
contributions of the role of the environment (e.g., habitat filtering), and of
biotic interactions (e.g., competitive exclusion), are inferred from the
distribution of taxa on a phylogeny composed from species occurring at larger
spatial scale. R packages and other software have been developed to generate
phylogenies from species lists using taxonomic information or DNA sequences
\citep[e.g.,][]{Webb2008,Pearse2013}. These phylogenies can then be used for
community phylogenetics analyses \citep[e.g.,][]{Pearse2015},
\citep{Kembel2010}, but they are often incomplete or not resolved enough. As OTL
becomes more comprehensive, and its taxonomic resolution increases, it could
become a valuable resource for ecologists seeking to use phylogenetic
information in their research.

@@

<<get_cats, purl=FALSE, fig.cap="Tree from \\citealt{Johnson2006} obtained from OTL">>=
cat_studies <- studies_find_studies(property = "ot:focalCladeOTTTaxonName",
                                    value = "Felidae", exact = TRUE)cat_studies
@
